\vspace{5em}On Evaluating Adversarial Robustness

### 2019-04-25 paper.tex
extra comment on random restarts and convergence

On at least a few inputs, confirm
that the number of iterations of gradient descent being performed is
sufficient by plotting the attack success and adversarial loss versus the number of
iterations.
%
This plots should eventually plateau; if not, the attack
has not converged and more iterations can be used until
it does. Plotting the adversarial loss is often more useful than plotting the attack success rate, as the former has a finer granularity and thus may reveal that the attack is still making progress even though the success rate seems to have plateaued.
The number of
iterations necessary is generally inversely proportional to step size and
proportional to distortion allowed.
%
Dataset complexity is often related.

@@

There are few reasonable threat models under which an attacker can
compute 100 iterations of gradient descent, but not 1000. As stated in~\cite{athalye2018obfuscated}, merely increasing the time it takes an adversary to find an adversarial example from one second to ten seconds does not constitute an increase in robustness.
%
Because the threat model must not constrain the approach an
attacker takes, it is worth evaluating against a strong attack
with many iterations of gradient descent.

@@

\paragraph{Start search from random offsets.}
%
When performing iterative attacks,
it is useful to begin the search for adversarial examples at random
offsets away from the initial, source input.
%
This can reduce the
distortion required to generate adversarial examples by 10\%
\citep{carlini2017towards}, and help avoid causing gradient masking
\citep{tramer2017ensemble,madry2017towards}.
%
Moreover, even if the attack uses sufficient iterations to converge, repeating the attack with multiple randomly chosen starting points decreases the likelihood of ending up in a sub-optimal local minima~\citep{madry2017towards,mosbach2018logit}.
%
Doing this
every time is not necessary, but doing it at least once to verify it
does not significantly change results is worthwhile.
%
Prior work has found that using at least 10 random starting points is effective.

@@

Further ensure that the iterative attack is properly converging, by verifying that increasing the number of iterations or the number of random restarts have no effect on the attack success rate and model loss.

>>>>

On at least a few inputs, confirm
that the number of iterations of gradient descent being performed is
sufficient by plotting the attack success and adversarial loss versus the number of
iterations.
%
This plots should eventually plateau; if not, the attack
has not converged and more iterations can be used until
it does. Plotting the adversarial loss is often more useful than plotting the attack success rate, as the former has a finer granularity and may reveal that the attack is still making progress even though the success rate seems to have plateaued.
The number of
iterations necessary is generally inversely proportional to step size and
proportional to distortion allowed.
%
Dataset complexity is often related.

@@

There are few reasonable threat models under which an attacker can
compute 100 iterations of gradient descent, but not 1000. As stated in~\cite{athalye2018obfuscated}, merely increasing the time it takes an adversary to find an adversarial example from one second to ten seconds does not constitute an increase in robustness.
%
Because the threat model must not constrain the approach an
attacker takes, it is worth evaluating against a strong attack
with many iterations of gradient descent, as well as many different random restarts (to avoid converging to sub-optimal local minima~\citep{madry2017towards,mosbach2018logit}).

@@

\paragraph{Start search from random offsets.}
%
When performing iterative attacks,
it is useful to begin the search for adversarial examples at random
offsets away from the initial, source input.
%
This can reduce the
distortion required to generate adversarial examples by 10\%
\citep{carlini2017towards}, and help avoid causing gradient masking
\citep{tramer2017ensemble,madry2017towards}.

Moreover, even if the attack uses sufficient iterations to converge, repeating the attack with multiple randomly chosen starting points decreases the likelihood of ending up in a sub-optimal local minima~\citep{madry2017towards,mosbach2018logit}.
%
Doing this
every time is not necessary, but doing it at least once to verify it
does not significantly change results is worthwhile.
%
Prior work has found that using at least 10 random starting points is effective.

@@

Another issue could be that the iterative attack is not converging properly.  A useful test is to verify that increasing the number of iterations or the number of random restarts have only marginal effect on the attack success rate and model loss.
